Effects of Water Permeability on the Hydrodynamics of a Vesicle Under Flow and Confinement

### 2020-12-20 vesicle_code/docs/permeableVes/main.tex
yny

\dropcap{W}ater balance is an essential process in the adaptation of a living cell to its environment \cite{AlbertsMolecularBiology}: Erythrocytes are known to  participate in efficient body water homeostasis by regulating its exchange of water  \cite{YangMaVerkman2001_JBC,SugieIntaglietta2018_AmJPhysiolHCP}.  Cells achieve motility by simultaneously regulating their cell volume and cell membrane tension through trafficking of aquaporin proteins \cite{SaadounPapadopoulosWatanabeEtAl2005_JCS,Verkman2008_JMM,BerthaudEtAl2016_SM} and flattening of caveolae \cite{Keren2011_EurBJ}. 
Cells also control water transport  as they activate shape fluctuations in the membrane for the bleb formation \cite{TaloniKardashSalmanEtAl2015_PRL}.

@@

Vesicles (self-enclosed lipid bilayer membranes) have been used as a model system to study reshaping, remodeling and scission of cell membranes due to osmotic stress \cite{OgleckaEtAl2014_eLife,CamposSaric2020_bioRxiv,Dimova2020_GVB,BhatiaChrist2020_SoftMatt}. Under an osmotic shock, a vesicle may undergo oscillatory variation in its enclosed volume \cite{ChabanonHoLiedberg2017_BJ}. When trapped in a microfluidic channel, an osmotic shock induces 
 vesicle shape changes, tank-treading and tumbling motions \cite{BhatiaRobinsonDimova2020_SoftMatt,BhatiaChrist2020_SoftMatt}, an illustration that the permeable water flow is inevitably coupled with the mechanical pressure jump across the membrane\cite{yao-mor2017}, which could become comparable to osmotic stress when the membrane deformation is large \cite{LiMoriSun2015_PRL,yao-mor2017}.  In this work we use numerical simulations to examine the hydrodynamics of a semipermeable vesicle in two dimensions. 
 It is challenging to keep a freely suspended vesicle in a steady flow for more than a few days. It is also difficult to quantify the change in vesicle area/volume in the experiments.
 Using numerical simulations we can quantify  the effects of water permeability on the hydrodynamics of a vesicle under mechanical stresses. 
 In the absence of an osmotic gradient, we first show that a freely suspended semipermeable vesicle behaves differently from an impermeable vesicle over a long time. Next we show that, at normal physiological conditions, the permeable water flow can be amplified by extreme confinement and results in observable change in both vesicle hydrodynamics and reduced area. 
 These results will shed light on the dynamic aging process of living cells that constantly go through flows and constrictions over a period of days.

>>>>

\dropcap{W}ater balance is an essential process in the adaptation of a living cell to its environment \cite{AlbertsMolecularBiology,YangMaVerkman2001_JBC,SugieIntaglietta2018_AmJPhysiolHCP,SaadounPapadopoulosWatanabeEtAl2005_JCS,Verkman2008_JMM,BerthaudEtAl2016_SM,Keren2011_EurBJ,TaloniKardashSalmanEtAl2015_PRL}. In response to external stimuli, cells move, deform, and release signaling molecules, such as ATP in red blood cells \cite{ZhangShenHoganBarakatMisbah2018_BJ} and cyclooxygenase-2 in endothelial cells \cite{Russell-PuleriPazAdams2016_AJHCP}. Water permeation is often assumed to play a negligible role in such chemomechanical processes, and yet recent findings suggest that both osmotic and mechanical stresses can induce water permeation that is significant enough for tumor cells to migrate under strong confinement \cite{StrokaJiangChenEtAl2014_Cell,LiMoriSun2015_PRL,yao-mor2017}, leading to a dynamic surface-to-volume ratio over time. To elucidate the effects of mechanically induced water permeation (which is a great challenge to quantify in experiments), in this work we use accurate numerical simulations to study the dynamic surface-to-volume ratio in a semi-permeable vesicle induced by mechanical stress.

%Cells also send out chemicals in response to 
%
% Erythrocytes are known to  participate in efficient body water homeostasis by regulating its exchange of water  \cite{YangMaVerkman2001_JBC,SugieIntaglietta2018_AmJPhysiolHCP}.  Cells achieve motility by simultaneously regulating their cell volume and cell membrane tension through trafficking of aquaporin proteins \cite{SaadounPapadopoulosWatanabeEtAl2005_JCS,Verkman2008_JMM,BerthaudEtAl2016_SM} and flattening of caveolae \cite{Keren2011_EurBJ}. 
%Cells also control water transport  as they activate shape fluctuations in the membrane for the bleb formation \cite{TaloniKardashSalmanEtAl2015_PRL}.
%
%
%%\dropcap{W}ater balance is an essential process in the adaptation of a living cell to its environment \cite{AlbertsMolecularBiology}: Erythrocytes are known to  participate in efficient body water homeostasis by regulating its exchange of water  \cite{YangMaVerkman2001_JBC,SugieIntaglietta2018_AmJPhysiolHCP}.  Cells achieve motility by simultaneously regulating their cell volume and cell membrane tension through trafficking of aquaporin proteins \cite{SaadounPapadopoulosWatanabeEtAl2005_JCS,Verkman2008_JMM,BerthaudEtAl2016_SM} and flattening of caveolae \cite{Keren2011_EurBJ}. 
%%Cells also control water transport  as they activate shape fluctuations in the membrane for the bleb formation \cite{TaloniKardashSalmanEtAl2015_PRL}.

@@

Vesicles (self-enclosed lipid bilayer membranes) have been used as a model system to study reshaping, remodeling and scission of cell membranes due to osmotic stress \cite{OgleckaEtAl2014_eLife,CamposSaric2020_bioRxiv,Dimova2020_GVB,BhatiaChrist2020_SoftMatt}. Under an osmotic shock, a vesicle may undergo oscillatory variation in its enclosed volume \cite{ChabanonHoLiedberg2017_BJ}. When trapped in a microfluidic channel, an osmotic shock induces 
 vesicle shape changes, tank-treading and tumbling motions \cite{BhatiaRobinsonDimova2020_SoftMatt,BhatiaChrist2020_SoftMatt}, an illustration that the permeable water flow is inevitably coupled with the mechanical pressure jump across the membrane\cite{yao-mor2017}, which could become comparable to osmotic stress when the membrane deformation is large \cite{LiMoriSun2015_PRL,yao-mor2017}.

 In this work we use numerical simulations to examine the hydrodynamics of a semipermeable vesicle in two dimensions. 
 It is challenging to keep a freely suspended vesicle in a steady flow for more than a few days. It is also difficult to quantify the change in vesicle area/volume in the experiments.
 Using numerical simulations we can quantify  the effects of water permeability on the hydrodynamics of a vesicle under mechanical stresses. 
 In the absence of an osmotic gradient, we first show that a freely suspended semipermeable vesicle behaves differently from an impermeable vesicle over a long time. Next we show that, at normal physiological conditions, the permeable water flow can be amplified by extreme confinement and results in observable change in both vesicle hydrodynamics and reduced area. 
 These results will shed light on the dynamic aging process of living cells that constantly go through flows and constrictions over a period of days.
